---
title: "report"
author: "interca"
date: "`r Sys.Date()`"
output: html_document
params:
  axis: NA
  axis_table: NA
---

InterCA dynamic report

Please find below an automatic report that has been produced according to your selections. Please notice that this report has been developed to facilitate faster interpretation of interpretive axes and interpretive planes as suggested at : ["Automatic" interpretation of multiple correspondence analysis (MCA) results for nonexpert users, using R programming \| Emerald Insight](https://www.emerald.com/insight/content/doi/10.1108/ACI-07-2022-0191/full/html)

Cite:

Moschidis, S., Markos, A., & Thanopoulos, A. C. (2022). "Automatic" interpretation of multiple correspondence analysis (MCA) results for nonexpert users, using R programming. Applied Computing and Informatics, ahead-of-print(ahead-of-print). <https://doi.org/10.1108/ACI-07-2022-0191>

According to your selections the following table is produced

```{r echo=FALSE}
library(pander)
params$axis
```

According to your selection the following table is produced
```{r echo=FALSE, render=pander::pander}
library(pander)
params$axis_table[1]->df
df=data.frame(df)
colnames(df)=c("Interpretive coordinates")
df
```

Acoording to your selection the most contributing (important) points of your axis is
```{r echo=FALSE}
library(tidyverse)
params$axis_table->df
df%>%filter(df>0)->right
df%>%filter(df<0)->left
cat(paste("Most contributing points on the left side of axis are:","\n"))
        cat(paste(rownames(left)))
cat(paste("Most contributing points on the right side of axis are:","\n"))
        cat(paste(rownames(right)))
```
